Keyword and Collocation analysis on India-related text of *Natural History*

### 2023-08-22 paper_quarto.qmd
0822 structure modification

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of *Natural History*"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
echo: false
warning: false
tbl-cap-location: top
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs keyword analysis and collocate examination techniques to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

@@

Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*, aiming to delve deeper into the themes associated with the Indian region referred in the text by employing keyword analysis and collocation analysis methods within the framework of corpus linguistics.

@@

To investigate the prominent themes in the India-related content discussed in *Natural History*, methods of keyword analysis and collocation analysis are employed for this study. Both of the analyses rely on the `mclm::assoc_scores` objects of the [mclm](https://github.com/masterclm/mclm) package, which return frequencies and association scores of a certain event in a target context and in a reference context.

@@

In conclusion, this paper located the research question on potential theme and topics in texts about India in Pliny the Elder's *Natural History* based on the prominent distribution of "India" in the entire text comparing to other place names. The analysis was conducted with the keyword analysis and collocation analysis in a framework of corpus linguistics.

>>>>

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of *Natural History*"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
echo: false
warning: false
tbl-cap-location: top
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs collocate examination techniques and keyword analysis to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

@@

Building upon this observation, the study focus is narrowed down to India-related text in *Natural History*, aiming to delve deeper into the themes associated with the Indian region referred in the text by employing collocation analysis and keyword analysis methods within the framework of corpus linguistics.

@@

To investigate the prominent themes in the India-related content discussed in *Natural History*, methods of collocation analysis and keyword analysis are employed for this study. Both of the analyses rely on the `mclm::assoc_scores` objects of the [mclm](https://github.com/masterclm/mclm) package, which return frequencies and association scores of a certain event in a target context and in a reference context.

@@

In conclusion, this paper located the research question on potential theme and topics in texts about India in Pliny the Elder's *Natural History* based on the prominent distribution of "India" in the entire text comparing to other place names. The analysis was conducted with the collocation analysis and keyword analysis in a framework of corpus linguistics.
